Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-06-30 paper/src/1_introduction.tex
modify 1,2,3

\section{Introduction}
\label{sec:introduction}
Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and low leatency interconnects.
%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.

One solution is federating a supercomputer with a public cloud,
and moving a part of jobs to the public cloud when there are not enough
computing nodes available for user's requests, which is known as \emph{cloud bursting}.
Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
and is employed by several private companies, 
there is a significant performance gap between supercomputers and clouds, 
there will still be several problems when we try to federate a supercomputer with a public cloud, 
and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
The biggest problem will be data transfer throughput between two environment, 
supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
low I/O throughput will suffer supercomputer user. This paper focuses on methodology 
of increasing throughput when we do federation.

>>>>

\section{Introduction}
\label{sec:introduction}
Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and low leatency interconnects.
%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
%Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
Although supercomputers can offer high capablity of computation, it is not unlimited, for some request peak, computation resource in supercomputer can not meet the needs of user, or simply user requesst more resource than supercomputers have, also some jobs require a exclusive usage for computing nodes, like grand challenge, will occpy a great amount of computation resource, leads inadequate of reourse for other job.
Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.

One solution is federating a supercomputer with a public cloud,
and moving a part of jobs to the public cloud when there are not enough
computing nodes available for user's requests, which is known as \emph{cloud bursting}.
Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
and is employed by several private companies, 
there is a significant performance gap between supercomputers and clouds, 
there will still be several problems when we try to federate a supercomputer with a public cloud, 
and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
The biggest problem will be data transfer throughput between two environment, 
since we want to move some jobs from supercomputer to public cloud, I/O data need to transfer between these two system, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
low I/O throughput will suffer supercomputer user. This paper focuses on methodology 
of increasing throughput when we do federation.

### 2014-06-30 paper/src/2_motivation.tex
modify 1,2,3

\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
  (1-4) [please add whatever you think it's needed]}
Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet.
Among many public cloud, Amazon Elastic Compute Cloud (Amazon EC2) is one of the most famous one, like other public cloud, Amazon EC2 privde VM computing nodes, distributed to several geographic regions.
Amazon EC2 provide a large amount of instance types optimized to fit different use cases comprise varying combinations of CPU, memory, storage, and networking capacity.
In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
About pricing, Amazon use a pay-as-you-go pricing policy, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
\subsection{Federation between supercomputers and clouds}
\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
                      (2-3) [please add whatever you think it's needed]}
Since there is a significate performance gap between supercomputer computing nodes and public cloud computing nodes.
We can not simply federate supercomputers with clouds, in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g. TSUBAME V queue with VM on clouds.
\subsection{Challenges in Federation with clouds}
\label{sec:problems}
\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
                              That's why the ``(B) perfomrance modeling`` is important}
Although we virtualize supercomputer and obtain a similiar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.

We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.

To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.

@@

using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
We provide a cost-based model to determine 
However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

>>>>

\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
  (1-4) [please add whatever you think it's needed]}
Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet, the main benefit of using a public cloud service are: easy fast and inexpensive set-up because hardware, application and bandwidth are covered by the provider, easy to scale to meet needs, no wasted resources because you pay for what you use.
There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 privdes Virtualize computing, and owns computing and data centers in several geographic regions.
Amazon EC2 provide a large amount of instance types optimized to fit different use cases comprise varying combinations of CPU, memory, storage, and networking capacity.
In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
Amazon EC2 charges for nodes usage, Amazon use a pay-as-you-go pricing policy\cite{AMAZON_AWS}, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
\subsection{Federation between supercomputers and clouds}
\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
                      (2-3) [please add whatever you think it's needed]}
When we try to federate supercomputer with public clouds, there are need to have a similiar performance and environment between these two systems.
So we virtualize the supercomputer(like TSUBAME V queue) and federate VMs running on supercomputers with VMs provided by public cloud.
By using VMs, we can run the same image on both supercomputer and public cloud as well as set both the same specification, and make it looks the same to user.%we can use in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g. TSUBAME V queue with VM on clouds.
\subsection{Challenges in Federation with clouds}
\label{sec:problems}
\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
                              That's why the ``(B) perfomrance modeling`` is important}
Although we virtualize supercomputer and obtain a similiar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.

We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
However, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.
For data-sensitive application, low I/O throughput is devastating, especially for application running on supercomputers, furthermore, lower I/O throughput leads a longer execution time, according to Amazon pay-as-you-go policy, longer execution time means more cost.

To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele

@@

%using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
%We provide a cost-based model to determine 
Fig.\ref{point to point connection AMAZON} shows the Ethernet throughput inside Amazon EC2 taken by using Iperf, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2.
Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
%Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.

### 2014-06-30 paper/src/3_burst_buffer.tex
modify 1,2,3

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system
\kento{how about read ?}.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

\subsection{Assumptions}
First, we make several assumptions for the federated environments as follows.
%For security consideration and the fact that IPv4 addresses becomes rare,
\begin{itemize}
	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
\end{itemize}

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.

Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
Buffer queue operation including data write back and operation when queue is full will be described in following section.

When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

@@

In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

@@

As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.

@@

On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.

@@

Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.

>>>>

An overview of I/O burst buffer architecture and two kinds of buffer model: one-side buffer and two-side buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through Ethernet.
In other cases (buffer queue is full when issue a write requst or requsted file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed. 
\kento{how about read ?}.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

@@

\subsection{Assumptions}
First, we make several assumptions for the federated environments as follows.
%For security consideration and the fact that IPv4 addresses becomes rare,
\begin{itemize}
	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
	\item All nodes used by the same job are allocated in the same system, since the Internet bandwidth is low and unstable, user do not want to make communication between nodes via Internet.% so data consistency can be guaranteed since that.
\end{itemize}

@@

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application and I/O burst buffer nodes.
Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.

Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O requset and send or receive I/O data.

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via Ethernet and can be seen among computing nodes in the same system after that.
However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to recieve new I/O data, causing a low I/O throughput.

%When I/O server is notified that buffer queue is ready,first, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
%Buffer queue operation including data write back and operation when queue is full will be described in following section.

Similiarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

@@

In this section we describe read and write operations when cache miss happens.%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

@@

As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be used to fully utilize the Internet bandwidth.

@@

On the contrary, two-side buffer solution uses I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.

@@

Compared with one-side buffer, %two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
%Also, 
two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

For these reasons, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
